Legends for Figures

### 2019-02-01 Manuscript/Figures/figure_legends.Rmd
updated figure and legend

**Figure 1: Model Construction.** Cell line specific Hi-C matices were obtained from [@rao20143d].  The linear genome was then binned according to the intervals of the square-symmetric contact matrices at given resolutions (10 kb, 25 kb, 50 kb, and 100 kb). The coordinates of subsequent topologically associating domains were identified using the Arrowhead TAD-calling algorithm [@durand2016juicebox]. Each TAD coordinate was then flanked by a unit-specific amount (in basepairs) respective to the resolution of the corresponding contact matrix. The response vector Y used for classification was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0). The spatial relationship between positional coordinates of various functional genomic elements, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.

>>>>

**Figure 1: Model Construction.** An illustration of the proposed model construction given cell line-specific Hi-C matrices obtained from [@rao20143d]. The contact matrix above is a visualization of the interconnectivity of chromosome 14 (GM12878) on the intervals from 20 mb to 100 mb [@durand2016juicebox]. The coordinates of subsequent topologically association domains were identified using the arrowhead algorithm from Juicer. The linear genome, represented by the diagonal of the contact matrix, was then binned according to prespecified interaction frequency resolutions (10 kb, 25 kb, 50 kb, and 100 kb). Each TAD coordinate was then flanked by a unit-specific amount (in basepairs) respective to the resolution of the corresponding contact matrix. The response vector Y, used for classification, was determined by whether a genomic bin overlapped with a flanked boundary region (Y=1) or not (Y=0). The spatial relationship between positional coordinates of various functional genomic annotations, obtained from ENCODE, and the genomic bins were then used to define the feature space of the models.
